---
title: "StemNav_R"
output: html_document
date: "2025-08-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Yale STEM Navigators - Crash Course in R

Below are a couple practice problems to review the topics covered in today's slides. There are also a couple new tidbits of information and tips specific to RStudio!

**Hint:** to run code chunks below, you can either press the green triangle at the top-right of the chunk, use *`Cmd + Enter`* on Mac, or *`Ctrl + Enter`* on Windows.

The answer key can be found **here**!

## Problem 1 (R Markdown in RStudio)

Below is a code chunk. This whole file is something called an "R-Markdown" file, which is a mix of different text formats alongside executable code blocks. The shortcut to insert a code block is *`Cmd + Option + I`* on Mac and *`Ctrl + Alt + I`* on Windows.

Highlight the italicized text below and input that shortcut to replace it with a code block. Add a comment inside that code block for good measure.

```{r}
# This is a comment! It's good practice to include these in your code as a form of documentation for future reference or for people collaborating with you. 
# That said, go ahead and replace the italicized text below with a code block
```

***Replace this text with a code chunk!***

## Problem 2 (Creating Objects)

Insert another code block below, then create and display the following:

1.  An object called *fifteen* which contains the number 15.
2.  A vector of length 3 called *pi* containing the digits 3, 1, and 4.
3.  A vector called *big_vec* containing all numbers from 1 to 100
    -   **Hint:** a consecutive sequence of numbers can be input via `x:y`, where `x` is the first number in the sequence, and `y` is the last number (e.g. `1:5` = `1, 2, 3, 4, 5`)
4.  A list containing the following elements:
    -   The character string `"python could never"`

    -   A vector of length 3 containing the logical values `TRUE, FALSE, TRUE`

    -   The number `1.2345`
5.  A 2x2 matrix containing the values `1, 2, 3, 4`

***Insert code block here***

## Problem 3 (Importing/Exploring a Data Frame)

Make a code block, and then create a data frame called *y_admits* using the CSV file linked [here](https://raw.githubusercontent.com/SebastianReyes2005/StemNav_R/refs/heads/main/Yale_Admit_Rates.csv). Display the first 5 rows, and then determine the

**Tip:** remember to include quotation marks around the link.

***Insert code block here***

```{r}
y_admits <- read.csv("https://raw.githubusercontent.com/SebastianReyes2005/StemNav_R/refs/heads/main/Yale_Admit_Rates.csv")

head(y_admits, n = 5)
```
